Missing data: Current practice in football research and recommendations for improvement

### 2020-09-05 paper/paper.Rmd
wording changes.

---
title: "Missing data: Current practice in football research and recommendations for improvement"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

2: University of New South Wales, Department of Statistics, School of
Mathematics and Statistics, Sydney, Australia.

3: Monash University, Department of Econometrics and Business Statistics,
Melbourne, Australia.

4: Australian Centre of Excellence for Mathematical and Statistical
Frontiers (ACEMS), Melbourne, Australia.

@@

>>>>

---
title: "Missing data: Current practice in football research and recommendations for improvement"
authors: David N Borg(1,2), Robert Nguyen(3), Nicholas J Tierney(4,5)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

2: Griffith University, School of Allied Health Sciences, Brisbane, Australia.

3: University of New South Wales, Department of Statistics, School of
Mathematics and Statistics, Sydney, Australia.

4: Monash University, Department of Econometrics and Business Statistics,
Melbourne, Australia.

5: Australian Centre of Excellence for Mathematical and Statistical
Frontiers (ACEMS), Melbourne, Australia.

@@

Missing data requires careful consideration across the entire analysis pathway. 
Here we present several practices to avoid.
